\documentclass[architecture.tex]{subfiles}
\begin{document}
This document outlines the software architecture for the 
web-based application \textit{Open Chess} that offers
an interactive chess board through a React Application
served with Flask. 
Using the application (playing a game of chess through mouse interaction),
the user is encouraged to explore the early-game strategies of the game of chess.
The backend of the application (written in Flask, with a SQLAlchemy database) 
internally evaluates positions and assigns them scores. 
The evaluation process is performed by Stockfish, a chess computer engine. 
Stockfish is used to assign scores to board positions fed to it, 
representing a move's soundness in the game. 
The scores for the initial and resulting board states in a move
form the weight of the move, taking into account 
other avaliable moves in the initial position.

The application defines \textit{book moves}, which are moves in certain
positions of the board that are known to be good.
These can be shown as arrows on the graphical board representation in the frontend,
and express their weights through their visual representation.

In the future, the viewing of book moves will be a feature for the player
to manage their known chess moves with the application, through exploring
variations of chess openings and adding new moves as they learn.

The app is intended for use as a training tool, prompting the player
to make good moves in pre-determined board positions.
This is meant to be gamified through assigning the a \textit{rank} to each move,
a value that varies with the player's prompted actions.
The player evaluation could be expanded to define an 
``experience point levelling'' type of gamification system, or a chess-style 
``Elo ranking'' type system.

The Open Chess source code is on \url{https://github.com/WilliamStenberg/open-chess},
and is Free Software.


\end{document}
